Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Add more in discussion on convergence

    \subsection{Convergence trouble}
        For a large number of particles and a low frequency the CCD-method get
        trouble with convergence. This happens as the confining potential $v
        \propto \omega^2$ will not be able to confine the particles when the
        interaction gets too strong. The CCD-method will in particular get a
        hard time keep the particles together as the excitation operator $t$
        only excites pairs of particles leading too strong increase in the
        interaction when the particles increase their energy level. This effect
        can potentially be somewhat alleviated by including the singles
        excitation, e.g., using the CCSD-method.

>>>>

    \subsection{Convergence trouble}
        For a large number of particles and a low frequency the CCD-method get
        trouble with convergence. This happens as the confining potential $v
        \propto \omega^2$ will not be able to confine the particles when the
        interaction gets too strong. The CCD-method will in particular get a
        hard time keep the particles together as the excitation operator $t$
        only excites pairs of particles leading to a too strong increase in the
        interaction when the particles increase their energy level. This effect
        can potentially be somewhat alleviated by including the singles
        excitation, e.g., using the CCSD-method.

        We can see this behaviour in our results. For $N = 2$ we get convergence
        for all methods for $\omega = 0.1$ shown in \autoref{tab:N2}. By
        increasing to $N = 6$ particles we immediately see how CCD with the HO
        basis will get in trouble for small values of $\omega$. By increasing
        the strength of the confinment even this method does converge.

        For $N = 6$ none of the methods converged when $\omega =
        0.1$\footnote{The RHF-method would probably have converged if we had
        started tuning its mixing parameter, but as we have focused on CCD we did
        not think it relevant to include these results.}. By increasing the
        frequency we restored the convergence. For larger number of shells we
        had to start increasing the value of $\theta \to 0.9$ in order to get
        convergence within the threshold.
